Proof equivalence in MLL is PSPACE-complete

### 2015-02-01 main/LMCS.tex
Edit final par of intro

The result that a canonical representation of multiplicative linear logic is essentially unfeasible raises the question, whether to turn to alternative notions of identity of proofs than that given by $*$-autonomous categories. The literature offers several interesting directions, including but not limited to \emph{polarised proof nets} \cite{Laurent-1999}, \emph{focused proof nets} \cite{Andreoli-Maieli-1999}, \emph{multi-focused proofs} \cite{Chaudhuri-Miller-Saurin-2008}, and Paul-Andr\'e Melli\`es's semantically appealing tensorial logic and dialogue categories \cite{Mellies-2012}.

>>>>

Since there can be no canonical representation of multiplicative linear logic proofs in accordance with the categorical semantics, it is tempting to consider other ways of defining the identity of proofs. The literature contains several interesting ideas in this direction, such as \emph{polarised proof nets} \cite{Laurent-1999}, \emph{focused proof nets} \cite{Andreoli-Maieli-1999}, \emph{multi-focused proofs} \cite{Chaudhuri-Miller-Saurin-2008}, and Paul-Andr\'e Melli\`es's semantically appealing \emph{tensorial logic} and \emph{dialogue categories} \cite{Mellies-2012}.
